OpenMP+Tapir: A Case Study of Using Tapir as a Common Parallel Intermediate Representation

### 2017-10-08 paper.tex
WTF?  almost every change I made resulted in a conflict

\title{OpenMPIR}
\subtitle{Implementing OpenMP tasks with Tapir}

@@

LLVM has gained traction in the broad community for its simplicity,
relative ease of both experimentation and modifications, and extensibility~\cite{lattner2004llvm}.
Historically, LLVM has only had a sequential semantics: there is no explicit notion
of concurrent or parallel processes. This has resulted in existing compilers
treating parallel constructs as thin wrappers for calls into run-time
systems. These calls are infeasible for the compiler to reason about because of
the complexity and flexibility of the runtimes being called, and the challenge
of reasoning about the corresponding semantics in a uniform fashion. The
addition of parallel constructs was recently explored by Schardl et
al.
%~\cite{tapir}.
By adding three first-class instructions to LLVM, Tapir
enables analyses and optimizations of parallel constructs. We briefly describe
the key aspects of Tapir in Section~\ref{Sec:Tapir}.
% I removed this as the reference was already given...   PM For a more complete
% description see \cite{tapir}.
% KD removed it again.  Also, citatations are meta-syntactic.

@@

problem, whose objective is to find a placement for $n$ queens on an $n \;
\times \; n$ chessboard such that none of the queens attack any other. It uses

@@

\section*{Acknowledgments}

Many thanks to Kei Davis for his excellent editing.

This work was supported by the Director, Office of Advanced Scientific
Computing Research, Office of Science, of the United States Department
of Energy, under the guidance of Dr. Sonia Sachs. This research was
supported by US National Science Foundation under CRII ACI 1565338,
CNS 1527076, and CNS 1217948 and by the Exascale Computing Project
(17-SC-20-SC), a collaborative effort of the U.S. Department of Energy
Office of Science and the National Nuclear Security Administration.
Los Alamos National Laboratory is managed and operated by Los Alamos
National Security, LLC (LANS), under contract number DE-AC52-06NA25396
for the Department of Energy's National Nuclear Security
Administration (NNSA).

>>>>

\title{OpenMP+Tapir: A Case Study of Using Tapir as a Common Parallel Intermediate Representation}

@@

LLVM has gained traction in the broad community for its simplicity,
relative ease of both experimentation and modifications, and extensibility~\cite{lattner2004llvm}.
Historically, LLVM has only had sequential semantics: there is no explicit notion
of concurrent or parallel processes. This has resulted in existing compilers
treating parallel constructs as thin wrappers for calls into run-time
systems. These calls are infeasible for the compiler to reason about because of
the complexity and flexibility of the runtimes being called, and the challenge
of reasoning about the corresponding semantics in a uniform fashion. The
addition of parallel constructs was recently explored by Schardl et
al.
%~\cite{tapir}.
By adding three first-class instructions to LLVM, Tapir
enables analyses and optimizations of parallel constructs. We briefly describe
the key aspects of Tapir in Section~\ref{Sec:Tapir}.
% I removed this as the reference was already given...   PM For a more complete
% description see \cite{tapir}.
% KD removed it again.  Also, citatations are meta-syntactic.

@@

problem, whose objective is to find a placement for $n$ queens on an $n
\times n$ chessboard such that none of the queens attack any other. It uses

@@

\section*{Acknowledgments}
Many thanks to Kei Davis for his excellent editing.

This work was supported by the Director, Office of Advanced Scientific
Computing Research, Office of Science, of the United States Department
of Energy, under the guidance of Dr. Sonia Sachs. This research was
supported by US National Science Foundation under CRII ACI 1565338,
CNS 1527076, and CNS 1217948 and by the Exascale Computing Project
(17-SC-20-SC), a collaborative effort of the U.S. Department of Energy
Office of Science and the National Nuclear Security Administration.
Los Alamos National Laboratory is managed and operated by Los Alamos
National Security, LLC (LANS), under contract number DE-AC52-06NA25396
for the Department of Energy's National Nuclear Security
Administration (NNSA). Additionally, this research was supported in
part by NSF Grants 1314547 and 1533644 and an MIT SuperUROP.
